Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-02-14 src/tex/ms.tex
reword M star opportunity

\subsection{An M~dwarf opportunity}
An interesting aspect lies in the distribution of host star properties, as different spectral types probe different past \gls{NUV} flux regimes.
FGK stars show a narrow distribution of maximum past \gls{NUV} fluxes in the \gls{HZ}, which may -- depending on the (unknown) threshold \gls{NUV} flux -- limit the diagnostic power of a survey.
In the case of a pure FGK sample, it will essentially only be sensitive to \gls{NUV} flux thresholds $\sim \SIrange{200}{400}{\erg\per\second\per\centi\meter\squared}$, and the chance of detecting biosignatures diminishes rapidly for higher thresholds within this range (see Figure~\ref{fig:inhabited_aafo_nuv_thresh}).
Detected biosignatures in an FGK sample would have little constraining power on testing the UV~Threshold Hypothesis; they would either suggest that low NUV fluxes are sufficient for abiogenesis or indicate a different abiogenic pathway~\citep[e.g.,][]{Westall2018}.
A lack of biosignatures in a larger FGK sample would support the UV~Threshold Hypothesis.

>>>>

\subsection{An M~dwarf opportunity}
An interesting aspect lies in the distribution of host star properties, as different spectral types probe different past \gls{NUV} flux regimes.
FGK stars \rev{exhibit a relatively} narrow \rev{range} of maximum past \gls{NUV} fluxes in the \gls{HZ}, which may -- depending on the (unknown) threshold \rev{flux} -- limit the diagnostic power of a survey.
\rev{A} pure FGK sample \rev{would} only be sensitive to \rev{flux} thresholds \rev{in the range of} $\sim\SIrange{200}{400}{\erg\per\second\per\centi\meter\squared}$.
\rev{A detection of biosignatures in such a sample would likely only suggest that either low \gls{NUV} fluxes are sufficient for abiogenesis or that an alternative abiogenic pathway may be at play~\citep[e.g.,][]{Westall2018}.
Conversely, a lack of biosignatures in a sufficiently large FGK sample could indicate that the actual threshold is higher than the maximum past flux levels reached by FGK hosts.
We further note that under the UV~Threshold Hypothesis, the fraction of inhabited planets in an FGK sample declines rapidly for increasing threshold fluxes, as shown in Figure~\ref{fig:inhabited_aafo_nuv_thresh}.
}
